Thesis Title

### 2022-03-17 chapters/introduction.tex
update

As explored in \secref{ssec:reads_2_genomes}, longer sequences are more informative than shorter sequencing data and can provide a more complete picture of the microbial community in a given samples.

@@

Longer sequences are more informative than shorter sequencing data and can provide a more complete picture of the microbial community in a given samples. Several dedicated metagenomic assembly tools are available, such as metaSPAdes (Nurk et al., 2017)  and MegaHIT (Li et al., 2015). These tools, in comparison to single-cell data assemblers, are better at dealing with the combination of intragenomic and intergenomic repeats and uneven sequencing coverage (Olson et al., 2017). Assembler using multiple k-mers, like the ones suggested, substantially outperform single k-mer assemblers, and smaller k-mers improve the recovery of low-abundance genomes, larger k-mer lead to a better recovery of highly abundant ones (Sczyrba et al., 2017). 

>>>>

As explored in \secref{ssec:reads_2_genomes}, longer sequences are more informative than shorter sequencing data, as the one obtained from second-generation sequencing (see \secref{ssec:2nd_gen_seq}), and can provide a more complete picture of the microbial community in a given samples. 
Several dedicated metagenomic assembly tools are available, such as metaSPAdes\footnote{\url{}}  and MegaHIT\footnote{\url{}} \citep{nurk_metaspades_2017, li_megahit_2015}. 
These tools, in comparison to single-cell data assemblers, are better at dealing with the combination of intragenomic and intergenomic repeats and uneven sequencing coverage \citep{olson_metagenomic_2017}.

@@
